Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added comment on Nmax

Finally, we remark that in the GR limit ($\gamma \to 0$)
the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
the Kerr QNMs for spins $\chi \lesssim 0.7$.
%
The values of the fitting coefficients $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$
can be found in Ref.~\cite{Maselli:2019mjd}, Table I.
%
The fitting coefficients for $N_{\rm max} = 9$, which extend the validity of
the spin-expansion up to $\chi \lesssim 0.99$ where obtained in
Ref.~\cite{Carullo:2021dui}.

>>>>

Finally, we remark that in the GR limit ($\gamma \to 0$)
the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
the Kerr QNMs for spins $\chi \lesssim 0.7$.
%
The values of the fitting coefficients $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$
can be found in Ref.~\cite{Maselli:2019mjd}, Table I.
%
In Ref.~\cite{Carullo:2021dui}, the fitting coefficients were calculated up to $N_{\rm max} = 9$,
which extend the validity of the spin-expansion up to $\chi \lesssim 0.99$.
%
As we will discuss in Sec.~\ref{sec:pe}, the expansion to $N_{\rm max} = 4$ is
sufficient for our purposes.
